Constraints on Assembly Bias from Galaxy Clustering

### 2016-06-16 ms.tex
Added discussion of Bayesian Information Criterion.

\usepackage{amssymb}
\usepackage{epsfig}
\usepackage{amsmath}
\usepackage{color}
\usepackage[dvipsnames]{xcolor}
\usepackage{hyperref}
\usepackage{yfonts}

@@

All of our analyses are based on the Bolshioi-Planck (BolshioP) simulation \citep{riebe_etal11}.
BolshoiP was run with cosmological parameters based on \citet{planck13}:
$\Omega_{\Lambda} = 0.693; \Omega_{\rm m} = 1 - \Omega_{\Lambda} = 0.307; \Omega_{\rm b} = 0.048;
h = 0.7; {\rm n_s}=0.96$; and $\sigma_8 = 0.82$. BolshoiP simulated the formation of structure within a cubic 
box $250$ ${\rm Mpc}/h$ on a side, requiring a particle mass of $m_{\rm p} = 1.35\times10^{8}M_{\odot}/h.$
Further information about the BolshoiP simulation is available at \url{https://www.cosmosim.org}.

@@

>>>>

\usepackage{amssymb}
\usepackage{epsfig}
\usepackage{amsmath}
\usepackage{color}
\usepackage[dvipsnames]{xcolor}
%\usepackage{hyperref}
\usepackage{yfonts}

@@

All of our analyses are based on the Bolshioi-Planck (BolshioP) simulation \citep{riebe_etal11}.
BolshoiP was run with cosmological parameters based on \citet{planck13}:
$\Omega_{\Lambda} = 0.693; \Omega_{\rm m} = 1 - \Omega_{\Lambda} = 0.307; \Omega_{\rm b} = 0.048;
h = 0.7; {\rm n_s}=0.96$; and $\sigma_8 = 0.82$. BolshoiP simulated the formation of structure within a cubic 
box $250$ ${\rm Mpc}/h$ on a side, requiring a particle mass of $m_{\rm p} = 1.35\times10^{8}M_{\odot}/h.$
Further information about the BolshoiP simulation is available at {\tt https://www.cosmosim.org}.

@@

Beyond the fit results, it is also possible to ask whether or not the fits to the data warrant the use of 
additional parameters (in this case, to describe assembly bias). This requires a metric that penalizes the 
use of additional parameters. A commonly used metric is the Bayesian Information Criterion 
\citep[BIC,][]{schwarz78}, defined as 
%
\begin{equation}
\mathrm{BIC} = -2 \mathcal{L}_{\rm max} + k\, \ln N, 
\end{equation}
%
where $\mathcal{L}_{\rm max}$ is the maximum of the likelihood, 
$k$ is the number of paramters in the model and $N$ is the number of 
data points. We compute the change in the BIC, $\Delta$BIC, by subtracting 
the BIC for the analysis with assembly bias from the BIC in the standard analysis 
in which there is no assembly bias. With this convention, $\Delta \mathrm{BIC} > 0$ 
favors assembly bias, suggesting that the data warrant the additional parametric freedom. 
Conversely, $\Delta \mathrm{BIC} < 0$ favors the standard analysis, 
suggesting that the additional freedom in the model does not improve the description of the data 
to a sufficiently great degree to support the added complexity. 
A common convention is to refer to the preference as 
{\em strong} when $\vert \Delta \mathrm{BIC}\vert \ge 5$.

The values of $\Delta$BIC are given in Table~\ref{table:bic}. In the analysis of the $\magr < -21$ sample, 
$\Delta \mathrm{BIC} < 0$, indicating that the additional parameters describing assembly bias are not 
warranted by the data. For all other samples, $\Delta \mathrm{BIC} > 0$, showing a preference for 
the models with assembly bias. The cases that most support the additional complexity 
of the decorated HOD are $\magr < -19$ and $\magr < -20$, for which $\Delta$BIC 
rises nearly to the level of a {\rm strong} preference.
